Quality measure notes

### 2021-08-10 StateOfPractice/Ao-Report/18Conclusion.tex
MI report - update ch 5 and other parts

With learnings from this project, we summarized recommendations for the future state of the practice assessments,
\begin{itemize}
	\item we can further automate the measurements on the grading temple in Appendix \ref{ap_grading_template}. For example, with automation scripts and a GitHub API, we may save significant time on retrieving the GitHub metrics;
	\item the grading standard can be more explicit. For example, we can explicitly define scores for each item in the grading temple.
	\item we can better organize the interview questions. We think they are good questions. However, since we use audio conversion tools to transcribe the answers, we should aim to make the transcription easier to read. For example, we can order them together for questions about the five software qualities and compose a similar structure for each.
	\item we can mark the follow-up interview questions with keywords. For example, say ``this is a follow-up question" every time asking one. Thus, we record this sentence in the transcription, and it will be much easier to distinguish the follow-up questions from the 20 designed questions.
\end{itemize}

>>>>

With learnings from this project, we summarized recommendations for the future state of the practice assessments:
\begin{itemize}
	\item we can further automate the measurements on the grading temple in Appendix \ref{ap_grading_template}. For example, with automation scripts and a GitHub API, we may save significant time on retrieving the GitHub metrics;
	\item the grading standard can be more explicit. For example, we can explicitly define scores for each item in the grading temple.
	\item we can improve some interview questions. For example, in question 14, ``Do you think improving this process can tackle the current problem?" is a yes-or-no question, which is not informative enough. As mentioned in Section \ref{sec_contribution_pm}, most interviewees ignored it. We can change it to ``By improving this process, what current problems can be tackled?"
	\item we can better organize the interview questions. Since we use audio conversion tools to transcribe the answers, we should aim to make the transcription easier to read. For example, we can order them together for questions about the five software qualities and compose a similar structure for each.
	\item we can mark the follow-up interview questions with keywords. For example, say ``this is a follow-up question" every time asking one. Thus, we record this sentence in the transcription, and it will be much easier to distinguish the follow-up questions from the 20 designed questions.
\end{itemize}

### 2021-08-10 StateOfPractice/Ao-Report/33InterviewAnswers.tex
MI report - update ch 5 and other parts

\noindent\textbf{Q1. Interviewees’ current position/title? degrees?}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Highest degree & Number of interviewees \\ \hline
PHD & 4 \\
Master & 3 \\
Bachelor & 0 \\
Unspecified academic degree & 2 \\ \hline
\end{tabular}
\caption{\label{tab_q1_degrees}Interviewees' highest academic degrees}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Major & Number of interviewees \\ \hline
Computer Science & 4 \\
Physics & 2 \\
Biomedical Engineering & 1 \\
Neuroimaging & 1 \\
Geology (image analysis) & 1 \\
Media Arts and Sciences & 1 \\
Mechanical Engineering & 1 \\
Materials Engineering & 1 \\
Psychology & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q1_majors}Interviewees' majors at university}
\end{table}

\noindent\textbf{Q2. Interviewees’ contribution to/relationship with the software?}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Role in the projects & Number of interviewees \\ \hline
Chief Architect & 2 \\
Lead Developer & 1 \\
Core Developer & 5 \\
Unspecified & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q2_roles}Interviewees' roles in the projects}
\end{table}

\noindent\textbf{Q3. Length of time the interviewee has been involved with this software?}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Length of time in the projects & Number of interviewees \\ \hline
0-1 & 1 \\
2-5 & 0 \\
6-10 & 2 \\
11-15 & 3 \\
16-20 & 2 \\
21-25 & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q3_years}Lengths of time that the interviewees worked in the projects}
\end{table}

\noindent\textbf{Q4. How large is the development group?}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Number of current members & Number of projects \\ \hline
1-3 & 5 \\
4-6 & 3 \\ \hline
\end{tabular}
\caption{\label{tab_q4_members}Numbers of current members in the projects}
\end{table}

@@

\noindent\textbf{Q6. What is the typical background of a developer?}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Background of a developer & Number of interviewees with the answer \\ \hline
\begin{tabular}[c]{@{}l@{}}Computer Science, Information\\ Technology, and Software Development \end{tabular} & 6 \\
Imaging & 2 \\
Medical Imaging & 1 \\
Mathematics & 1 \\
Biomedical Engineering & 1 \\
Computer Aided Medical Procedures & 1 \\
Physician & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q6_dev_backgrounds}Backgrounds of developers by the numbers of interviewees with the answers}
\end{table}

\noindent\textbf{Q7. What is your estimated number of users? How did you come up with that estimate?}

@@

\begin{table}[H]
\centering
\begin{tabular}{lll}
\hline
Software & Rough estimation & Considered facts \\ \hline
3D Slicer & 100,000 & \begin{tabular}[c]{@{}l@{}} Search results on Google Scholar;\\ number of new posts per year on slicer.org; \\ number of downloads. \end{tabular} \\
INVESALIUS 3 & 75,000 & Number of random IDs created by new installation.\\
dwv & No estimation & About 20 companies integrated \textit{dwv} in their products. \\
BioImage Suite Web & 100 active users & \begin{tabular}[c]{@{}l@{}}  The  interviewee only counted the users from \\ several Universities who were active users. \end{tabular} \\
ITK-SNAP & 10,000 plus & Number of downloads. \\
MRIcroGL & No estimation & \begin{tabular}[c]{@{}l@{}}  It is the top 1 downloaded software on this NITRC list \\ \hyperlink{https://www.nitrc.org/top/toplist.php?type=downloads}{https://www.nitrc.org/top/toplist.php?type=downloads} \end{tabular} \\
Weasis & \begin{tabular}[c]{@{}l@{}}  10,000 user used \\ it as least once \end{tabular} & Number of profiles. \\
OHIF & About 5000 & \begin{tabular}[c]{@{}l@{}}   Some platforms integrated \textit{OHIF}, and it was hard \\ to know the number of end users. \end{tabular} \\ \hline
\end{tabular}
\caption{\label{tab_q7_num_users}Rough Estimations for the Number of Users}
\end{table}

@@

\noindent\textbf{Q8. What is the typical background of a user?}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Background of a user & Number of interviewees with the answer \\ \hline
Medical Researchers & 6 \\
Doctors/Health care professionals/Surgeons & 5 \\
Student Researchers & 4 \\
Patients & 3 \\
Paleontologist & 1 \\
Biomechanical Engineers & 1 \\
Imaging Researchers & 1 \\
Mechanical Engineers & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q8_user_backgrounds}Backgrounds of users by the numbers of interviewees with the answers}
\end{table}

>>>>

\begin{description}
\item[Q1.] Interviewees’ current position/title? degrees?
\end{description}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Highest degree & Num ans. \\ \hline
PHD & 4 \\
Master & 3 \\
Bachelor & 0 \\
Unspecified academic degree & 2 \\ \hline
\end{tabular}
\caption{\label{tab_q1_degrees}Interviewees' highest academic degrees}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Major & Num ans. \\ \hline
Computer Science & 4 \\
Physics & 2 \\
Biomedical Engineering & 1 \\
Neuroimaging & 1 \\
Geology (image analysis) & 1 \\
Media Arts and Sciences & 1 \\
Mechanical Engineering & 1 \\
Materials Engineering & 1 \\
Psychology & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q1_majors}Interviewees' majors at university}
\end{table}

\begin{description}
\item[Q2.] Interviewees’ contribution to/relationship with the software?
\end{description}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Role in the projects & Num ans. \\ \hline
Chief Architect & 2 \\
Lead Developer & 1 \\
Core Developer & 5 \\
Unspecified & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q2_roles}Interviewees' roles in the projects}
\end{table}

\begin{description}
\item[Q3.] Length of time the interviewee has been involved with this software?
\end{description}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Years & Num ans. \\ \hline
0-1 & 1 \\
2-5 & 0 \\
6-10 & 2 \\
11-15 & 3 \\
16-20 & 2 \\
21-25 & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q3_years}Lengths of time that the interviewees worked in the projects}
\end{table}

\begin{description}
\item[Q4.] How large is the development group?
\end{description}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Num mbrs & Num ans. \\ \hline
1-3 & 5 \\
4-6 & 3 \\ \hline
\end{tabular}
\caption{\label{tab_q4_members}Numbers of current members in the projects}
\end{table}

@@

\begin{description}
\item[Q6.] What is the typical background of a developer?
\end{description}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Background of a developer & Num ans. \\ \hline
\begin{tabular}[c]{@{}l@{}}Computer Science, Information\\ Technology, and Software Development \end{tabular} & 6 \\
Imaging & 2 \\
Medical Imaging & 1 \\
Mathematics & 1 \\
Biomedical Engineering & 1 \\
Computer Aided Medical Procedures & 1 \\
Physician & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q6_dev_backgrounds}Backgrounds of developers by the numbers of interviewees with the answers}
\end{table}

\begin{description}
\item[Q7.] What is your estimated number of users? How did you come up with that estimate?
\end{description}

@@

\begin{table}[H]
\centering
\hspace*{-2cm}\begin{tabular}{lll}
\hline
Software & Rough estimation & Considered facts \\ \hline
3D Slicer & 100,000 & \begin{tabular}[c]{@{}l@{}} 1) search results on Google Scholar;\\ 2) number of new posts per year on slicer.org; \\ 3) number of downloads. \end{tabular} \\
INVESALIUS 3 & 75,000 & Number of random IDs created by new installation.\\
dwv & No estimation & About 20 companies integrated \textit{dwv} in their products. \\
BioImage Suite Web & 100 active users &  Only counted the active users from several Universities. \\
ITK-SNAP & 10,000 plus & Number of downloads. \\
MRIcroGL & No estimation & The top 1 downloaded software on the NITRC list. \\
Weasis & 10,000 incl. one-time users & Number of profiles. \\
OHIF & About 5000 & Some platforms integrated \textit{OHIF}; hard to estimate. \\ \hline
\end{tabular}
\caption{\label{tab_q7_num_users}Rough Estimations for the Number of Users}
\end{table}

@@

\begin{description}
\item[Q8.] What is the typical background of a user?
\end{description}

@@

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Background of a user & Num ans. \\ \hline
Medical Researchers & 6 \\
Doctors/Health care professionals/Surgeons & 5 \\
Student Researchers & 4 \\
Patients & 3 \\
Paleontologist & 1 \\
Biomechanical Engineers & 1 \\
Imaging Researchers & 1 \\
Mechanical Engineers & 1 \\ \hline
\end{tabular}
\caption{\label{tab_q8_user_backgrounds}Backgrounds of users by the numbers of interviewees with the answers}
\end{table}
